---
title: "The Within-Reliability Diagnostic"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The Within-Reliability Diagnostic}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
run <- requireNamespace("fixest", quietly = TRUE)
```

`ferobust` implements a within-reliability diagnostic. For a continuous, slow-moving regressor in a panel regression with
unit and year fixed effects, it asks how much of the shrinkage from pooled OLS to
fixed effects is measurement-error attenuation rather than confounding removed,
and reports an identified set rather than a single coefficient.

## A worked example

The package ships a small synthetic panel, `panel_demo`, with a slow-moving,
mismeasured regressor `x` and its measurement-model posterior standard deviation
`x_sd`.

```{r, eval = run}
library(ferobust)
data(panel_demo)
head(panel_demo)
```

The whole workflow is one call. With `reliability = "auto"`, the package finds the
posterior column (`x_sd`, or a `_codelow`/`_codehigh` credible interval) and
computes the reliability itself, so the analyst supplies no reliability number:

```{r, eval = run}
audit(y ~ x | unit + year, data = panel_demo,
      key_var = "x", reliability = "auto", re = FALSE)
```

The output reports the empirical ICC of the regressor, pooled OLS and fixed
effects, the corrected within-reliability, the identified set, the Imbens-Manski
confidence interval, and a verdict. Here the bounds exclude zero, so the case is a
**rescue**: the fixed-effects estimate is attenuated, and the corrected bounds
recover an effect that the bare coefficient understated.

## The corrected formula

The diagnostic rests on the corrected within-reliability,

$$\lambda_w = \frac{\lambda - \widehat{\mathrm{ICC}}}{1 - \widehat{\mathrm{ICC}}},$$

where $\lambda$ is the overall reliability of the regressor and
$\widehat{\mathrm{ICC}}$ is its empirical intraclass correlation in the sample.
This is the Griliches-Hausman within-reliability rewritten in terms of the
observable ICC: under classical measurement error
$\widehat{\mathrm{ICC}} = \mathrm{ICC}^* \cdot \lambda$, and substituting gives the
corrected form.

## Reliability without a measurement model

When no posterior or external reliability is available, the autocorrelation
frontier bounds $\lambda_w$ from the regressor's own persistence under an assumed
ceiling on how persistent the measurement error could be:

```{r, eval = run}
frontier_audit(y ~ x | unit + year, data = panel_demo,
               key_var = "x", psi_max = c(0, 0.5, 0.7))
```

## The routing rule

A sign test routes each application. When pooled OLS and fixed effects share a
sign and fixed effects is smaller, the result is the identified set across the
defensible reliability range: a rescue if it excludes zero, not identified if it
does not. When fixed effects is larger in magnitude, the case is a complement and
the bounds become a one-sided floor. When the signs disagree, the bounds do not
apply and fixed effects is reported as a within-unit estimate. When reliability
cannot be defended, the frontier asks whether measurement error could account for
the shrinkage at all.

## See also

The working paper develops the corrected formula, the routing
rule, and the partial-identification bounds, and applies them to a worked
bureaucracy-and-growth case plus a broader audit of canonical panel studies.
